Return Oriented Programming

### 2023-02-11 presentation.tex
changes

\section{How to find suitable Gadgets?}
\begin{frame}
    \begin{itemize}
    \item Search gadgets
    \end{itemize}
    \bltCommand{ropcommand.sh}{Dumping Gadgets}{dumpgadget}
    \begin{itemize}
        \item 34011 Gadgets - 716,056 kB binary
        \item Most of them are not very useful but the sheer size makes it likely we have suitable candidates, using regular expressions we can find suitable candidates fast
        \item Example 1: pop edx $\rightarrow$ \regex{\^{}.* pop edx ; .*ret}
        \item Example 2: int 0x80 $\rightarrow$ \regex{\^{}.* int 0x80}
        \item Example 3: xor eax, eax $\rightarrow$ \regex{\^{}.* xor eax, eax ; .*ret}
    \end{itemize}
\end{frame}

\section{Example: Open a shell}
\subsection{Target Program and Compilation}
\begin{frame}[fragile]
    \frametitle{Target Program and Compliation}
    \bltCode{vuln.c}{c}{Target Program (stack protectors must be off)}{targetprogram}
    \bltCommand{compilation.sh}{Compilation command}{comp}
\end{frame}
\subsection{General approach}
\begin{frame}[fragile]
    \frametitle{Spawning a shell: Approach}
    \begin{itemize}
        \item Using ropper we can find our desired gadgets
        \item Lets say we want to execute a shell using execve, for that we need to accomplish the following goals
        \begin{enumerate}
            \item write /bin/sh into memory (at the data segment)
            \item init systemcall number (11)
            \item init systemcall argument (address of /bin//sh)
            \item call systemcall
        \end{enumerate}
    \end{itemize}
\end{frame}
\subsection{Generating the payload}
\begin{frame}[fragile]
    \frametitle{Generating the payload, writing /bin}
    \begin{lstlisting}[style=code, language=python]
from struct import pack

>>>>

\section{How to find suitable Gadgets?}
\begin{frame}
    \frametitle{How to find suitable Gadgets?}
    \begin{itemize}
    \item Multiple methods, using the tools directly you can search gadgets of your liking, but we can also dump them into a file and search using regular expressions.
    \end{itemize}
    \bltCommand{ropcommand.sh}{Dumping Gadgets}{dumpgadget}
    \begin{itemize}
        \item Most of them are not very useful because they are very specific, amount compensates for that 716 kB binary $\rightarrow$ 34011 Gadgets
        \item Example 1: pop edx $\rightarrow$ \regex{\^{}.\{0,10\}pop edx ;.\{0,10\}ret}
        \item Example 2: int 0x80 $\rightarrow$ \regex{\^{}.\{0,10\}int 0x80}
        \item Example 3: xor eax, eax $\rightarrow$ \regex{\^{}.\{0,10\}xor eax, eax ;.\{0,10\}ret}
    \end{itemize}
\end{frame}

\section{Example: Open a shell}
\subsection{Target Program and Compilation}
\begin{frame}[fragile]
    \frametitle{Target Program and Compliation}
    \bltCode{vuln.c}{c}{Target Program (stack protectors must be off)}{targetprogram}
    \bltCommand{compilation.sh}{Compilation command}{comp}
\end{frame}
\subsection{General approach}
\begin{frame}[fragile]
    \frametitle{Spawning a shell: Approach}
    \begin{itemize}
        \item Using ROPgadget we can find our desired gadgets
        \item Lets say we want to execute a shell using execve, for that we need to accomplish the following goals
        \begin{enumerate}
            \item write /bin/sh into memory (at the data segment)
            \item init systemcall number (11)
            \item init systemcall argument (address of /bin//sh)
            \item call systemcall
        \end{enumerate}
        \item All of this has to be done using Bytes that are not \Verb+\\0x00+ because thats the character used for identifying the end of a string.
    \end{itemize}
\end{frame}
\subsection{Generating the payload}
\begin{frame}[fragile]
    \frametitle{Generating the payload, writing /bin}
    \begin{lstlisting}[style=code, language=python]
from struct import pack
